Vragenlijst thesis evaluatie

### 2015-02-15 doc/template/chap-1.tex
intro gametheory

%\chapter{Intoduction to GameTheory}
%\label{cha:1}
\documentclass[10pt]{article}
\begin{document}

In this chapter an introduction to gametheory will be given with the formulas that will be used troughout this paper. We start with the basics of gametheory. People that have a background in gametheory can skip this chapter.

>>>>

\chapter{Intoduction to GameTheory}
\label{cha:1}
%\documentclass[10pt]{article}
%\begin{document}

\section{Intro Game Theory}

%begin over dat gametheorie handig is in de economie
In the following paragraph an introduction to game theory is given based on the work of \todo{werk van Essentials of Game Theory} and \todo{Coursera game theory}.
Game theory studies the interaction between independent and self-interested agents. For this reason it is very important for economics and also for politics, biology, computer science, philosophy and a variety of other disciplines. It is a mathematical way of modelling the interactions between two or more agents where the outcome depends on what everybody does and how it should be structured to lead to good outcomes. \\
%Every agent has different levels of happiness for the different outcomes.
A self-interested independent agent does not necessarily mean that they want to harm other agents or that they only care about themselves. Each agent has preferences about the states of the world he likes. These preferences are mapped to natural numbers and are called the utility function. The numbers are interpreted as a mathematical measure to tell you how much an agent likes or dislikes the states of the world. It also explains the impact of uncertainty. When an agent is uncertain about a distribution of outcomes, his utility will describe the expected value of the utility function with respect to the probability of the distribution of the outcomes. For example: with 0.7 probability it will be 7 degrees outside and 0.3 probability it will be 10 degrees. The agent can have a different opinion about that distribution versus another distribution. (\todo{uitleggen aan de hand van een voorbeeld}).\\

A game in game theory consists of multiple agents and every agent has a set of actions that he can play. 
%self interested meaing

%utility function meaning

%Cooperative and non cooperative games

% example of a game

\section{Other}
In this chapter an introduction to gametheory will be given with the formulas that will be used troughout this paper. We start with the basics of gametheory. People that have a background in gametheory can skip this chapter.
